RNA-seq from 4 cell populations

### 2021-08-02 deconvolution/fans4/molec_profiling.Rmd
bug fix

ggplot(df_cv_FANS, aes(log2(sqrt(total)), color=key)) + geom_density(size=2) + theme_bw(15) + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5), legend.position="right")  + scale_color_manual(values=colorCodes) + xlab(bquote(log[2]~CV))

@@

  # isexpr = rowSums(edgeR::cpm(gtex_count[,id])>1) >= 0.1*ncol(gtex_count[,id])
  isexpr = filterByExpr(geneCounts[,id], model.matrix(~CellType, info[id,]))

@@

ggplot( df_melt, aes(key, value, fill=key)) + geom_bar(stat='identity') + theme_bw(10) + theme(aspect.ratio=5, plot.title = element_text(hjust = 0.5), legend.position="none")  + scale_fill_manual(values=c(colsGTEx, colorCodes)[levels(df3$key)]) + coord_flip() + ylab("# genes expressed") + scale_y_continuous(expand=c(0,0)) + xlab('') + facet_wrap(~variable)

>>>>

ggplot(df_cv_FANS, aes(log2(sqrt(total)), color=key)) + geom_density(size=2) + theme_bw(15) + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5), legend.position="right")  + scale_color_manual(values=colorCodes) + xlab(bquote(log[2]~CV))
```

```{r include.gtex}

@@

  # isexpr = rowSums(edgeR::cpm(gtex_count[,id])>1) >= 0.1*ncol(gtex_count[,id])
  isexpr = filterByExpr(gtex_count[,id], model.matrix(~SMTSD, gtex_sample[id,]))

@@

ggplot( df_melt, aes(key, value, fill=key)) + geom_bar(stat='identity') + theme_bw(10) + theme(aspect.ratio=5, plot.title = element_text(hjust = 0.5), legend.position="none")  + scale_fill_manual(values=c(colsGTEx, colorCodes)[levels(df3$key)]) + coord_flip() + ylab("# genes expressed") + scale_y_continuous(expand=c(0,0)) + xlab('') + facet_wrap(~variable)
```
